---
title: "final group project rmd"
author: "Group 10"
date: "11/29/2021"
output: html_document
---

## Introduction 

## Statement of Purpose 

## Background and Preparation

## Methodology 

## Results and Conclusions

### Required Packages
```{r packages}
library(ggwordcloud)
library(tidyverse)
library(urbnmapr)
library(janitor)
library(ggplot2)
library(skimr)
library(sf)
```

### Loading the data 
```{r loading the data}
calories <- read_csv('data/fastfood_calories.csv') %>%
  clean_names() %>%
  rename(total_prot=protein) %>%
  mutate(restaurant=str_replace_all(tolower(restaurant), '[^\\w]', '')) %>%
  filter(
    !is.na(fiber),
    !is.na(total_prot),
    restaurant %in% c('mcdonalds', 'burgerking', 'tacobell', 'subway')) %>%
  select(-x1, -vit_a, -vit_c, -calcium, -salad)

restaurants <- read_csv('data/FastFoodRestaurants.csv') %>%
  clean_names() %>%
  mutate(
    state=if_else(province == 'Co Spgs', 'CO', province),
    name=str_replace_all(tolower(name), '[^\\w]', '')) %>%
  filter(name %in% unique(calories$restaurant)) %>%
  select(-address, -country, -keys, -postal_code, -province, -websites)

abbrevs <- read_csv('data/state-abbrevs.csv') %>%
  clean_names()

population <- read_csv('data/us_pop.csv') %>%
  clean_names() %>%
  left_join(abbrevs, by='state') %>%
  select(-state) %>%
  rename(state=abbreviation)
```

### Plot 1: US Map of 

### Plot 2: 
### Plot 3: Vegetarian and Pescetarian friendly restaurants
```{r vegetarian and pescetarian plots}
#Vegetarian 
calories_veg <- calories %>% 
  mutate(item=str_replace_all(tolower(item), '[^\\s\\w]',''),
        wo = ifelse(grepl('wo chicken', item), 1, 0),
         veggie = ifelse(grepl('veggie', item), 1, 0),
        veggies = ifelse(grepl('veggies', item), 1, 0),
        cheesepizza = ifelse(grepl('cheese pizza', item),1,0),
        cheesequesadilla = ifelse(grepl('cheese quesadilla', item),1,0),
        cheeserollup = ifelse(grepl('cheese rollup', item),1,0),
        bean_burrito = ifelse(grepl('bean burrito', item),1,0),
        tostada = ifelse(grepl('spicy tostada', item),1,0),
        gardensalad = ifelse(grepl('side garden salad', item),1,0),
         total_veg = wo + veggie + veggies + cheesepizza + cheesequesadilla + cheeserollup + bean_burrito + tostada + gardensalad) %>%
  group_by(restaurant) %>% 
  summarize(count = n(),
            sum_veg = sum(total_veg), 
            perc = sum_veg/count * 100) 
calories_veg

# R vegetarian friendly plot 
veggie_plot <- 
  calories_veg %>% ggplot(aes(x= reorder(restaurant, perc), y = perc, fill=factor(ifelse(restaurant=="subway","Highlighted","Normal")))) + 
  geom_col() + 
  theme(legend.position = "none")+
  ggtitle("Subway is the most vegetarian friendly restaurant") +
  xlab("Restaurants") + 
  ylab("Percentage of menu items that are pescetarian friendly (%)") 
veggie_plot

#Pescetarian 
calories_pesc <- calories %>% 
  mutate(item=str_replace_all(tolower(item), '[^\\s\\w]',''),
         wo = ifelse(grepl('wo chicken', item), 1, 0),
         veggie = ifelse(grepl('veggie', item), 1, 0),
         veggies = ifelse(grepl('veggies', item), 1, 0),
         cheesepizza = ifelse(grepl('cheese pizza', item),1,0),
         cheesequesadilla = ifelse(grepl('cheese quesadilla', item),1,0),
         cheeserollup = ifelse(grepl('cheese rollup', item),1,0),
         bean_burrito = ifelse(grepl('bean burrito', item),1,0),
         tostada = ifelse(grepl('spicy tostada', item),1,0),
         gardensalad = ifelse(grepl('side garden salad', item),1,0),
         seafood = ifelse(grepl('seafood', item),1,0),
         tuna = ifelse(grepl('tuna', item),1,0),
         fish = ifelse(grepl('fish', item),1,0),
         lobster = ifelse(grepl('lobster', item),1,0),
         total_pesc = wo + veggie + veggies + cheesepizza + cheesequesadilla + cheeserollup + bean_burrito + tostada + gardensalad + seafood + tuna + fish + lobster) %>%
  group_by(restaurant) %>% 
  summarize(count = n(),
            sum_pesc = sum(total_pesc), 
            perc = sum_pesc/count * 100)
calories_pesc

# R pescetarian friendly plot 
fishie_plot <- 
  calories_pesc %>% ggplot(aes(x= reorder(restaurant, perc), y = perc, fill=factor(ifelse(restaurant=="subway","Highlighted","Normal")))) + 
  geom_col() + 
  theme(legend.position = "none")+
  ggtitle("Subway is the most pescetarian friendly restaurant") +
  xlab("Restaurants") + 
  ylab("Percentage of menu items that are pescetarian friendly (%)")
fishie_plot 
```

## Discussion and Critique



```{r}

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
