---
title: "final group project rmd"
author: "Group 10"
date: "11/29/2021"
output: html_document
---

## Introduction 


## Statement of Purpose 
To create intuitive visualizations that will allow consumers to make quick and informative choices about their meals when going to one of the four fast food restaurants we focused on for this project. We try to include information that will allow diverse consumers (ex: vegetarian/pescetarian, health-conscious) to come to their own conclusion about which meal from which restaurant they should get for their next meal. 

## Background and Preparation
We utilized 4 separate data sets to create our visualizations: 

- Fast food menu items 

data source 
what preparation we did 

## Methodology 

## Results and Conclusions

### Required Packages
```{r packages}
library(ggwordcloud)
library(tidyverse)
library(urbnmapr)
library(janitor)
library(ggplot2)
library(skimr)
library(sf)
```

### Loading the data 
```{r loading the data}
calories <- read_csv('data/fastfood_calories.csv') %>%
  clean_names() %>%
  rename(total_prot=protein) %>%
  mutate(restaurant=str_replace_all(tolower(restaurant), '[^\\w]', '')) %>%
  filter(
    !is.na(fiber),
    !is.na(total_prot),
    restaurant %in% c('mcdonalds', 'burgerking', 'tacobell', 'subway')) %>%
  select(-x1, -vit_a, -vit_c, -calcium, -salad)

restaurants <- read_csv('data/FastFoodRestaurants.csv') %>%
  clean_names() %>%
  mutate(
    state=if_else(province == 'Co Spgs', 'CO', province),
    name=str_replace_all(tolower(name), '[^\\w]', '')) %>%
  filter(name %in% unique(calories$restaurant)) %>%
  select(-address, -country, -keys, -postal_code, -province, -websites)

abbrevs <- read_csv('data/state-abbrevs.csv') %>%
  clean_names()

population <- read_csv('data/us_pop.csv') %>%
  clean_names() %>%
  left_join(abbrevs, by='state') %>%
  select(-state) %>%
  rename(state=abbreviation)
```

### 1: Calorie distribution 
*Question answered:* What is the distribution of calories for each restaurant? 

```{r}

```

### 2: Balance score boxplot 
*Question answered:* What is the distribution of balance scores? 

```{r}

```

### 3: Healthiest menu items 
*Question answered:* Which menu items from which restaurants are the healthiest? 

```{r}

```

### 4: Wordcloud 
*Question answered:* 
```{r}

```

### 5: Vegetarian and Pescetarian friendly restaurants
*Question answered:* Which of the four fast food restuarants is most vegetarian and or pescetarian friendly? 

In this section, we explored the calories data set to find which restaurant is most vegetarian and or pescetarian friendly 

```{r vegetarian and pescetarian plots}
#Vegetarian 
calories_veg <- calories %>% 
  mutate(item=str_replace_all(tolower(item), '[^\\s\\w]',''),
        wo = ifelse(grepl('wo chicken', item), 1, 0),
         veggie = ifelse(grepl('veggie', item), 1, 0),
        veggies = ifelse(grepl('veggies', item), 1, 0),
        cheesepizza = ifelse(grepl('cheese pizza', item),1,0),
        cheesequesadilla = ifelse(grepl('cheese quesadilla', item),1,0),
        cheeserollup = ifelse(grepl('cheese rollup', item),1,0),
        bean_burrito = ifelse(grepl('bean burrito', item),1,0),
        tostada = ifelse(grepl('spicy tostada', item),1,0),
        gardensalad = ifelse(grepl('side garden salad', item),1,0),
         total_veg = wo + veggie + veggies + cheesepizza + cheesequesadilla + cheeserollup + bean_burrito + tostada + gardensalad) %>%
  group_by(restaurant) %>% 
  summarize(count = n(),
            sum_veg = sum(total_veg), 
            perc = sum_veg/count * 100) 
calories_veg

# R vegetarian friendly plot 
veggie_plot <- 
  calories_veg %>% ggplot(aes(x= reorder(restaurant, perc), y = perc, fill=factor(ifelse(restaurant=="subway","Highlighted","Normal")))) + 
  geom_col() + 
  theme(legend.position = "none")+
  ggtitle("Subway is the most vegetarian friendly restaurant") +
  xlab("Restaurants") + 
  ylab("Percentage of menu items that are pescetarian friendly (%)") 
veggie_plot

#Pescetarian 
calories_pesc <- calories %>% 
  mutate(item=str_replace_all(tolower(item), '[^\\s\\w]',''),
         wo = ifelse(grepl('wo chicken', item), 1, 0),
         veggie = ifelse(grepl('veggie', item), 1, 0),
         veggies = ifelse(grepl('veggies', item), 1, 0),
         cheesepizza = ifelse(grepl('cheese pizza', item),1,0),
         cheesequesadilla = ifelse(grepl('cheese quesadilla', item),1,0),
         cheeserollup = ifelse(grepl('cheese rollup', item),1,0),
         bean_burrito = ifelse(grepl('bean burrito', item),1,0),
         tostada = ifelse(grepl('spicy tostada', item),1,0),
         gardensalad = ifelse(grepl('side garden salad', item),1,0),
         seafood = ifelse(grepl('seafood', item),1,0),
         tuna = ifelse(grepl('tuna', item),1,0),
         fish = ifelse(grepl('fish', item),1,0),
         lobster = ifelse(grepl('lobster', item),1,0),
         total_pesc = wo + veggie + veggies + cheesepizza + cheesequesadilla + cheeserollup + bean_burrito + tostada + gardensalad + seafood + tuna + fish + lobster) %>%
  group_by(restaurant) %>% 
  summarize(count = n(),
            sum_pesc = sum(total_pesc), 
            perc = sum_pesc/count * 100)
calories_pesc

# R pescetarian friendly plot 
fishie_plot <- 
  calories_pesc %>% ggplot(aes(x= reorder(restaurant, perc), y = perc, fill=factor(ifelse(restaurant=="subway","Highlighted","Normal")))) + 
  geom_col() + 
  theme(legend.position = "none")+
  ggtitle("Subway is the most pescetarian friendly restaurant") +
  xlab("Restaurants") + 
  ylab("Percentage of menu items that are pescetarian friendly (%)")
fishie_plot 
```

## Discussion and Critique

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
